Beyond clines: lineages and haplotype blocks in hybrid zones

### 2016-04-25 drafts/review-responses-april-2016.tex

\begin{point}{}
    From a theoretical perspective, the article makes modest but valid contributions, and  Equation 4 and 5 are potentially interesting extensions to equation (1). The practical benefit of using these equations rather than forward simulations appears limited.
\end{point}

\reply
\alisa{This is a point we have considered ourselves. We present these equations as a way of building our model up to address haplotype lengths. Both analytical expressions and simulations are presented so that they each support the conclusions of the other.} \yb{However, we also believe that analytical results can allow for a deeper understanding than simulation output. 
To aid our readers in developing this understanding, we have gone through considerable pains to map terms in our equations to the biological processes of migration, selection and recombination. 
We believe that our efforts will help build a better mechanistic understanding in our readers in addition to making them aware of our results.}

\begin{point}{}
    While reading the manuscript, I found it difficult to distinguish the most important observations from more tangential observations. The manuscript reads like a long list of observations, and would benefit from more focus on the main findings and more structure.
\end{point}

\reply
\yb{We agree that a long set of theoretical results can be tedious. We have therefore reshaped the introduction to highlight our major question ``How does selection against incompatibilities in a hybrid zone influence the length distribution of ancestry tracts?'' }

@@

\begin{point}{Eq.\ref{eqn:g_pde}}
If $a<b<\theta<0$, then I interpret $g(\theta,b) = 0$. If correct, this should be specified.  Alternately, the bounds of the integral could be modified to account for this situation.
\end{point}

\reply
Thanks for catching the mistake; we modified the bounds of the integral.

\begin{point}{}
As an example of a section that felt unstructured, consider the discussion starting at l.347.  This long paragraph starts with a long list of observations, without giving a hint as to where we are going. Beginning the paragraph with the main idea for the paragraph would be useful.
\end{point}

\reply
We added an introductory sentence here to provide some structure. We have also gone through to clarify other sections that felt unclear.

### 2016-04-25 drafts/hybrid_zone.tex
added blockLengthPlots

The resulting equation is similar to \eqref{eqn:q_pde} with a term added for branching,
which is written (omitting the $(x,t)$ for conciseness):
\begin{align}
    \begin{aligned} \label{eqn:g_pde}
        \frac{d}{dt} g_A(a,b) 
        &= G^A g_A(a,b) + r(a,b) (1-p) (g_A(a,b)-g_B(a,b))
            \\ {} & \qquad 
            + (1-p) \left( 
                \int_a^{\min(0,b)} g_B(a,\theta) g_A(\theta,b) d\theta
                + \int_{\max(0,a)}^b g_A(a,\theta) g_B(\theta,b) d\theta 
            \right)
            \\ {} & \qquad 
            + p \int_a^b {
                g_A(a,\theta) g_A(\theta,b) 
            } d\theta
            - (b-a) g_A(a,b)  ,
    \end{aligned} 
\end{align}
\alisa{Need to be related to Figure 1}
Here the first term ($G^A g_A$) represents spatial mixing,
and the second term results from recombinations \emph{between} the block and the selected site 
in heterozygotes, which switch the identity of the linked, selected locus \alisa{without splitting the block}
(the factor $(1-p)$ is the probability that the block, initially linked to an $A$ allele, encounters a $B$ allele
under the assumption of locally random mating).
In the integrals, $\theta$ is the genomic position of the recombination event occuring \emph{inside} the block.
The third term accounts for such recombinations in a heterozygote: 
the portion of the block nearest the selected site remains linked to an $A$ allele, 
and the remaining portion becomes linked to a $B$ allele (as is the case in the most recent recombination event shown in Fig.~\ref{Fig:schematic}).
\alisa{to account for cases where the selected locus lies outside the interval [a,b],} 
we say that the integral $\int_a^{\min(0,b)}$ is zero if  $a>0$ 
and likewise $\int_{\max(0,a)}^b$ is zero if $b<0$.
The last integral results from recombination inside the block in homozygotes for $A$ (as is the case for the second recombination event in Fig.~\ref{Fig:schematic}),
and the final term balances the outflux due to all recombinations.
The equation for $g_B(x,t;a,b)$ is identical after exchanging $A \leftrightarrow B$ and
$p \leftrightarrow (1-p)$.
The boundary conditions are $g_A(x,0;a,b)=1$ and $g_B(x,0;a,b)=0$.

>>>>

The resulting equation is similar to \eqref{eqn:q_pde} with a term added for branching,
which is written (omitting the $(x,t)$ for conciseness):
\begin{align}
    \begin{aligned} \label{eqn:g_pde}
        \frac{d}{dt} g_A(a,b) 
        &= G^A g_A(a,b) + r(a,b) (1-p) (g_A(a,b)-g_B(a,b))
            \\ {} & \qquad 
            + (1-p) \left( 
                \int_a^{\min(0,b)} g_B(a,\theta) g_A(\theta,b) d\theta
                + \int_{\max(0,a)}^b g_A(a,\theta) g_B(\theta,b) d\theta 
            \right)
            \\ {} & \qquad 
            + p \int_a^b {
                g_A(a,\theta) g_A(\theta,b) 
            } d\theta
            - (b-a) g_A(a,b)  ,
    \end{aligned} 
\end{align}
Here the first term ($G^A g_A$) represents spatial mixing,
and the second term results from recombinations \emph{between} the block and the selected site 
in heterozygotes, which switch the identity of the linked, selected locus \alisa{without splitting the block}
(the factor $(1-p)$ is the probability that the block, initially linked to an $A$ allele, encounters a $B$ allele
under the assumption of locally random mating).
In the integrals, $\theta$ is the genomic position of the recombination event occuring \emph{inside} the block.
The third term accounts for such recombinations in a heterozygote: 
the portion of the block nearest the selected site remains linked to an $A$ allele, 
and the remaining portion becomes linked to a $B$ allele (as is the case in the most recent recombination event shown in Fig.~\ref{Fig:schematic}).
\alisa{to account for cases where the selected locus lies outside the interval [a,b],} 
we say that the integral $\int_a^{\min(0,b)}$ is zero if  $a>0$ 
and likewise $\int_{\max(0,a)}^b$ is zero if $b<0$.
The last integral results from recombination inside the block in homozygotes for $A$ (as is the case for the second recombination event in Fig.~\ref{Fig:schematic}),
and the final term balances the outflux due to all recombinations.
The equation for $g_B(x,t;a,b)$ is identical after exchanging $A \leftrightarrow B$ and
$p \leftrightarrow (1-p)$.
The boundary conditions are $g_A(x,0;a,b)=1$ and $g_B(x,0;a,b)=0$.
